\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.15in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\newtheorem*{proposition}{Proposition}

\title{The Cubic Surface Discriminant in Clebsch--Salmon Invariants}
\author{}
\date{}

\begin{document}
\maketitle

Let $S \subset \mathbf P^3$ be a cubic surface over a field of characteristic zero,
and let
\[
(A,B,C,D,E)=(I_8,I_{16},I_{24},I_{32},I_{40})
\]
denote the Clebsch--Salmon invariants in the standard normalization.  The
Clebsch-normalized discriminant is the following weighted homogeneous polynomial
of degree $32$ in the coefficients of the cubic surface.

\begin{proposition}
With the above normalization,
\[
\boxed{\
\Delta_{\mathrm{Cl}}
= (A^2-64B)^2 - 2^{11}(8D+AC).
}
\]
Equivalently,
\[
\Delta_{\mathrm{Cl}}
= A^4 - 128A^2B + 4096B^2 - 2048AC - 16384D.
\]
In particular, the invariant $E$ does not enter the formula.
\end{proposition}

For comparison with the pentahedral form, write a general cubic surface as
\[
S_{(a_0,\ldots,a_4)}:\qquad
\sum_{i=0}^4 a_i X_i^3=0,\qquad \sum_{i=0}^4 X_i=0,
\]
and let $\sigma_j$ be the elementary symmetric polynomial of degree $j$ in
$a_0,\ldots,a_4$.  In this convention the fundamental invariants are
\[
A=\sigma_4^2-4\sigma_3\sigma_5,
\qquad
B=\sigma_1\sigma_5^3,
\qquad
C=\sigma_4\sigma_5^4,
\qquad
D=\sigma_2\sigma_5^6,
\qquad
E=\sigma_5^8.
\]
Substitution gives exactly the discriminant formula above; this is Lemma 2.6
of Elsenhans--Jahnel \cite{EJ}.  They also note that the formula is classical,
due to Salmon, but that the version printed by Salmon contained a misprint later
corrected by Edge \cite{Edge}.

Thus, in this normalization, $S$ is singular precisely when
\[
\Delta_{\mathrm{Cl}}=0.
\]
If instead one uses the resultant-normalized discriminant of the quaternary cubic
form, the expression above must be multiplied by the fixed nonzero scalar dictated
by that normalization.

\begin{thebibliography}{9}

\bibitem{EJ}
A.-S. Elsenhans and J. Jahnel,
\emph{The discriminant of a cubic surface},
Geom. Dedicata \textbf{159} (2012), 29--40.
\href{https://doi.org/10.1007/s10711-011-9643-7}{doi:10.1007/s10711-011-9643-7}.

\bibitem{Edge}
W. L. Edge,
\emph{The discriminant of a cubic surface},
Proc. Roy. Irish Acad. Sect. A \textbf{80} (1980), 75--78.

\end{thebibliography}

\end{document}
